Modelling the gas kinematics of an atypical Lyman-alpha emitting compact dwarf galaxy

### 2017-09-13 paper/paper.tex
additional boldface

Qualitatively this result can be understood as follows.
Due to the large fraction of \lya photons being emitted within the
moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile closely follows 
the clump kinematics. 
In other words, the width of the intrinsic line
is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$, {\bf the exponent defining
  the steepness of the radial velocity profile. } 
Furthermore, the relatively low mean number of clumps per line of
sight, $0.8<f_{\mathrm{cl}}<8$, combined with the high velocity dispersion
of the clumps implies existence of low-density inter-clump 
regions where \lya photons can freely propagate.
This gives result to an emergent spectrum close to the intrinsic one, explaining the high
flux at the line's center.

>>>>

Qualitatively this result can be understood as follows.
Due to the large fraction of \lya photons being emitted within the
moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile closely follows 
the clump kinematics. 
In other words, the width of the intrinsic line
is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$, {\bf the exponent defining
  the steepness of the radial velocity profile. } 
{\bf Furthermore, the relatively low mean number of clumps per line of
sight, $0.8<f_{\mathrm{cl}}<8$,} combined with the high velocity dispersion
of the clumps implies existence of low-density inter-clump 
regions where \lya photons can freely propagate.
This gives result to an emergent spectrum close to the intrinsic one, explaining the high
flux at the line's center.
